---
title: "An example of set visualisation"
author: "Eliora Henzler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview for SetViz}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = "~/..")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Vignette Info
The vignette shows how to use the main functions of the package and the graph you can expect afterward. 


## Quickstart guide
Below is an example of how to calculate set intersections from the Iraq MSNA 2018 with REACH.

```{r, results='hide', message=FALSE}
library("Setviz")
library("dplyr")
library("survey")
library("UpSetR")
```

### Preparation
```{r, warning = FALSE}
#Load your data
#Fix the names that you want intersections for 
varnames <- c("Food",	"Health",	"WASH",	"Education",	"Protection",	"Shelter",	"Livelihoods") 
#The variables in the dataframe should all be 1s and 0s or T/F
data[,varnames] %>% str 
```

### Calculating intersections and making the plot, using make_set_percentages
In this case, we are not interested in single variables (no intersection) and we want to see 10 intersections in total

```{r, fig.show='hold'}
plot_set_percentages(data, varnames, "weight_nat", 10, exclude_unique = T, "PIN_Intersections")
```

## Calculating multiple set intersections with a plot for each, using lapply
To save the same plot for different groups in your dataset, define which variable you want to disaggregate by. The different plots can be saved as jpeg or pdf. 

```{r, fig.show='hold'}

data$hh_type %>% table
by <- "hh_type"

split.data.frame(data, data[[by]]) %>% lapply(function(x){
  label <- paste0(unique(x[[by]]),"PIN_intersections")
    plot_set_percentages(x, varnames,  "weight_nat", 10, exclude_unique = T, label)
    })

```
