---
title: "quickstart"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Setviz)
```


## Example data
Start with a dataset with logical or binary 0/1 columns:

```{r}

data[,c("WASH","Protection","Education","Shelter","Livelihoods")] %>% head


```

## Basic Plot

You can create the intersection plot directly:

```{r}

plot_set_percentages(data = data,
                     varnames = c("WASH","Protection","Education","Shelter","Livelihoods"),
                     nintersects = 12)

```

## Cummulative vs. Exclusive sets

By default, the sets are calcualted _cumulatively_. This means that in this example in this example, the set "Wash & Shelter" also includes all records that are in "Wash & Shelter & Livelihoods".

To prevent this behaviour and have exact, mutually exclusive sets (meaning that "Wash & Shelter" contains exclusively the records that are TRUE for Wash and shelter _and FALSE for all other variables_), you can set the `mutually_exlusive_sets` parameter to `TRUE`:

```{r}
plot_set_percentages(data = data,
                             varnames = c("WASH","Protection","Education","Shelter","Livelihoods"),nintersects = 12,
                             mutually_exclusive_sets = TRUE)

```


## Include single category sets

To include sets of a single category (no intersection but only one of the binary data variables are 1/TRUE), set `exclude_unique` to `FALSE`.

```{r}

plot_set_percentages(data = data,
                             varnames = c("WASH","Protection","Education","Shelter","Livelihoods"),nintersects = 12,
                             exclude_unique = FALSE)

```


As you see above, if you are using cumulative sets, the single-category sets will always be larger than combinations that contain them. This option makes most sense with mutually exclusive sets:

```{r}
plot_set_percentages(data = data,
                             varnames = c("WASH","Protection","Education","Shelter","Livelihoods"),nintersects = 12,
                             mutually_exclusive_sets = TRUE,
                             exclude_unique = FALSE)
```

## IMPORTANT NOTES

- For complex samples that require weighted percentages, you need to provide the `weight_variable` or the `weight_function` paramter. (please see `?plot_set_percentages` for details.)
- The "Set Size" on the bottom left may _not be correct_ and should not be included in any published outputs.
- Currently decimal percentages are not supported. Therefore sets with <=0.5% share will be ignored. You can instead treat them as 1% by setting `round_to_1_percent` to `TRUE`





